Reproduce anaylses of Beninca et al (2008)

### 2016-02-19 code/report.Rmd
fix

The datasets are read from this github repository:
```{r}
repo <- "https://raw.githubusercontent.com/opetchey/ReScience-submission/beninca_dev"
```

>>>>

The datasets are read from this github repository:
```{r}
repo <- "https://raw.githubusercontent.com/opetchey/ReScience-submission/petchey-plebani-pennekamp-2016"
```
